library(tidyverse)
nhl <- read_csv("nhl_pit_sj_game6.csv")
str(nhl)



```{r}
sjs <- nhl %>%
  filter(shot_attempt == 1, team == "San Jose Sharks") %>%
  mutate(x_cord = x_cord*(-1))
pitt <- nhl %>%
  filter(shot_attempt == 1, team == "Pittsburgh Penguins") %>%
  mutate(x_cord = x_cord)

nhl_shots <- bind_rows(sjs, pitt)

nhl_shots %>%
  filter(!is.na(event_type)) %>%
  ggplot(aes(x = x_cord, y = y_cord, col = event_type, hjust = -.3, shape = event == "goal")) +
  geom_point(alpha = 0.8) +
  theme_bw() + 
  labs(title = "Stanley Cup 2016 Game 6 Shot Chart",
       subtitle = "           San Jose Sharks                         Pittsburgh Penguins") +
  scale_x_continuous(name="X Location") +
  scale_y_continuous(name="Y Location") +
  labs(shape = NULL, color = "Shot Type") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_shape_manual(labels = c("Shot on Net", "Goal"), values = c(16, 4)) +
  scale_color_manual(labels = c("Backhand", "Deflected", "Slap Shot", "Snap Shot", "Tip-In", "Wrap-Around", "Wrist Shot"), values = c("chartreuse", "red", "brown", "cyan", "darkorange1", "deeppink", "blue")) +
  coord_fixed() +
  ggsave("shotchart.png")


## change colors to team colors
## reflect sharks on left and penguins oon right of vertical line
## add shot type as size? or color scale
## denote goals with text
## impose over rink image 



```


```{r}
## graphing shot increase after penalties 
## line graph (need to fix hms time to numeric and then mutate so that vertical lines can be added). add shading for penalty length
install.packages("ggpubr")
library(ggpubr)
theme_set(theme_pubr())

nhl_1 <- tibble()
nhl_1 <- nhl %>%
  filter(period == 1) %>%
  mutate(new_time = period_time)
nhl_2 <- nhl %>%
  filter(period == 2) %>%
  mutate(new_time = period_time + 20)
nhl_3 <- nhl %>%
  filter(period == 3) %>%
  mutate(new_time = period_time + 40)

nhl_all <- rbind(nhl_1, nhl_2, nhl_3)

nhl$period_time <- as.numeric(nhl$period_time)
nhl$period_time <- nhl$period_time / 60
nhl$period_time

nhl$cumulative_shots <- cumsum(nhl$shot_attempt)

nhl_all %>%
  ggplot(aes(x = new_time, y = cumulative_shots)) +
  geom_line() +
  geom_rect(
    aes(xmin = 7.8333, xmax = 9.8333, ymin = 0, ymax = Inf), alpha = 0.005, fill = "cyan") +
  geom_rect(
    aes(xmin = 45.4333, xmax = 47.4333, ymin = 0, ymax = Inf), alpha = 0.005, fill = "yellow") + 
  geom_rect(
    aes(xmin = 51.0333, xmax = 53.0333, ymin = 0, ymax = Inf), alpha = 0.005, fill = "cyan") +
  geom_rect(
    aes(xmin = 59.8333, xmax = 60, ymin = 0, ymax = Inf), alpha = 0.005, fill = "yellow") +
  labs(title = "Shot Increase over the Duration of Power Plays",
       x = "Time",
       y = "Total Shots") +
  theme(plot.title = element_text(hjust = 0.5)) +
   ggsave("EDAline.png")
             

```
```{r}
nhl$hits <- nhl$event == "hit"
nhl$giveaway <- nhl$event == "giveaway"
nhl$hits <- as.integer(nhl$hits)
nhl$giveaway <- as.integer(nhl$giveaway)
nhl$takeaway <- nhl$event == "takeaway"
nhl$takeaway <- as.integer(nhl$takeaway)
nhl$shot <- nhl$event == "shot"
nhl$shot <- as.integer(nhl$shot)
nhl$blocked_shot <- nhl$event == "blocked_shot"
nhl$blocked_shot <- as.integer(nhl$blocked_shot)

nhl_hit <- data.frame("player_one" = nhl$player_one, "hits" = nhl$hits)
nhl_giveaway <- data.frame("player_one" = nhl$player_one, "giveaway" = nhl$giveaway)
nhl_takeaway <- data.frame("player_one" = nhl$player_one, "takeaway" = nhl$takeaway)
nhl_shot <- data.frame("player_one" = nhl$player_one, "shot" = nhl$shot)
nhl_blocked_shot <- data.frame("player_one" = nhl$player_one, "blocked_shot" = nhl$blocked_shot)


nhl_hit_total <- tibble()

nhl_hit_total <- nhl_hit %>%
  filter(hits == 1)
nhl_hit_total <- as.data.frame(table(nhl_hit_total$player_one))

nhl_giveaway_total <- nhl_giveaway %>%
  filter(giveaway == 1)
nhl_giveaway_total <- as.data.frame(table(nhl_giveaway_total$player_one))

nhl_takeaway_total <- nhl_takeaway %>%
  filter(takeaway == 1)
nhl_takeaway_total <- as.data.frame(table(nhl_takeaway_total$player_one))

nhl_shot_total <- nhl_shot %>%
  filter(shot == 1)
nhl_shot_total <- as.data.frame(table(nhl_shot_total$player_one))

nhl_blocked_shot_total <- nhl_blocked_shot %>%
  filter(blocked_shot == 1)
nhl_blocked_shot_total <- as.data.frame(table(nhl_blocked_shot_total$player_one))

nhl_cluster <- merge(nhl_hit_total, nhl_giveaway_total, by = "Var1", all = TRUE)
nhl_cluster_2 <- merge(nhl_takeaway_total, nhl_cluster, by = "Var1", all = TRUE)
nhl_cluster_3 <- merge(nhl_shot_total, nhl_blocked_shot_total, by = "Var1", all = TRUE )
nhl_cluster_4 <- merge(nhl_cluster_2, nhl_cluster_3, by = "Var1", all = TRUE)
nhl_cluster_4[is.na(nhl_cluster_4)] = 0
nhl_cluster_4$minimax_clusters <- NULL
nhl_cluster_4$full_minimax_clusters <- NULL

nhl_cluster_4$Hits <- nhl_cluster_4$Freq.x.x
nhl_cluster_4$Giveaways <- nhl_cluster_4$Freq.y.x
nhl_cluster_4$Takeaways <- nhl_cluster_4$Freq
nhl_cluster_4$Shots <- nhl_cluster_4$Freq.x.y
nhl_cluster_4$Blocked_Shots <- nhl_cluster_4$Freq.y.y
nhl_cluster_4$Freq <- NULL
nhl_cluster_4$Freq.x.x <- NULL
nhl_cluster_4$Freq.x.y <- NULL
nhl_cluster_4$Freq.y.x <- NULL
nhl_cluster_4$Freq.y.y <- NULL
nhl_cluster_4$Player <- nhl_cluster_4$Var1
nhl_cluster_4$Var1 <- NULL
## minimax
install.packages("protoclust")
library(protoclust)
install.packages("ggthemes")
library(ggthemes)
## for 2
nhl_multidim_clust <- protoclust(dist(dplyr::select(nhl_cluster_2,
                                                    Freq, Freq.x)))
plot(nhl_multidim_clust)

minimax_player_clusters <- 
  protocut(nhl_multidim_clust, k = 3)
nhl_cluster_2 <- nhl_cluster_2 %>%
  mutate(minimax_clusters = 
           as.factor(minimax_player_clusters$cl))
nhl_cluster_2 %>%
  ggplot(aes(x = Freq.x, y = Freq,
             color = minimax_clusters)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  theme_bw() +
  labs(x = "giveaways",
       y = "hits",
       color = "cluster") +
  theme(legend.position = "bottom")

minimax_player_clusters$protos

## for 5
nhl_cluster_4 <- nhl_cluster_4[-c(2),]

nhl_multidim_clust <- protoclust(dist(dplyr::select(nhl_cluster_4,
                                                    Hits, Giveaways, Takeaways, Shots, Blocked_Shots)))
plot(nhl_multidim_clust)
nhl_multidim_clust_cut <- protocut(nhl_multidim_clust, k = 3)

install.packages("GGally")
library(GGally)
nhl_cluster_4 <- nhl_cluster_4 %>%
  mutate(full_minimax_clusters = 
           as.factor(nhl_multidim_clust_cut$cl))
ggpairs(nhl_cluster_4,
        columns =
          c("Hits", "Giveaways",
            "Takeaways", "Shots", "Blocked_Shots"),
        aes(color = full_minimax_clusters)) +
  labs(title = "Game Event Clustering of Position/Role") +

install.packages("gt")
library(gt)

gt(dplyr::select(nhl_cluster_4[minimax_player_clusters$protos, ],
              Player, Hits, Giveaways, Takeaways, Shots, Blocked_Shots))
## heir for categories
nhl_hclust <- 
  hclust(dist(
    dplyr::select(nhl_cluster,
                  Freq.x, Freq.y)),
         method = "complete")
plot(nhl_hclust)

hc_player_clusters <- 
  cutree(nhl_hclust,
         k = 3)
nhl_cluster <- nhl_cluster %>%
  mutate(player_hc_clusters =
           as.factor(hc_player_clusters))
nhl_cluster %>%
  ggplot(aes(x = Freq.x, y = Freq.y, color = player_hc_clusters)) +
  geom_point() +
  theme_bw()

## possesion
nhl <- nhl[!is.na(nhl$x_cord),]
nhl <- nhl[!is.na(nhl$y_cord),]

nhl_hclust_pos <- 
  hclust(dist(
    dplyr::select(nhl,
                  x_cord, y_cord)),
         method = "complete")
plot(nhl_hclust)

hc_player_clusters_pos <- 
  cutree(nhl_hclust_pos,
         k = 3)
nhl <- nhl %>%
  mutate(player_hc_clusters_pos =
           as.factor(hc_player_clusters_pos))
nhl %>%
  ggplot(aes(x = x_cord, y = y_cord, color = player_hc_clusters_pos)) +
  geom_point() +
  theme_bw()
```

